showData 4

### 2016-11-01 CreateData/creDat.Rnw
fix errors with causes

<<getdata>>=
source("calWin.R")
library(xtable)
library(knitr)
library(eha)
library(skum)
library(dplyr)
library(tidyr)
load("../../../Data/adult.rda")
adult <- calWin(adult, c(1851, 1951))
source("R/addPer.R")
adult <- addPer(adult, cuts = seq(1851, 1951, by = 25))
adult <- rc(adult)
## NEW hisclass, 6 + 7 --> 6:
adult$hisclass[!is.na(adult$hisclass) & (adult$hisclass == 7)] <- 6
## Recode to four classes:
hisc <- adult$hisclass
    hisc[is.na(hisc)] <- -1
    x <- hisc
    hisc[x %in% 1:2] <- 1
    hisc[x %in% 3:4] <- 2
    hisc[x == 5] <- 3
    hisc[x >= 5.9] <- 4
    is.na(hisc) <- hisc == -1
    adult$hisclass <- hisc

@@

vb <- rbind(aduu, foli)
x <- with(vb, table(period, hisclass, useNA = "ifany"))
y <- prop.table(x, margin = 1) * 100
print(xtable(round(y, 1), digits = 0, caption = "Hisclass by time period, 1901--2013 (per cent)."))
@

>>>>

<<getdata>>=
source("calWin.R")
library(xtable)
library(knitr)
library(eha)
library(skum)
library(dplyr)
library(tidyr)
library(stringr)
load("../../../Data/adult.rda")
adult <- calWin(adult, c(1851, 1951))
source("R/addPer.R")
adult <- addPer(adult, cuts = seq(1851, 1951, by = 25))
adult <- rc(adult)
## NEW hisclass, 6 + 7 --> 6:
adult$hisclass[!is.na(adult$hisclass) & (adult$hisclass == 7)] <- 6
## Recode to four classes:
hisc <- adult$hisclass
    hisc[is.na(hisc)] <- -1
    x <- hisc
    hisc[x %in% 1:2] <- 1
    hisc[x %in% 3:4] <- 2
    hisc[x == 5] <- 3
    hisc[x >= 5.9] <- 4
    is.na(hisc) <- hisc == -1
    adult$hisclass <- hisc

@@

vb <- rbind(aduu, foli)
vb$period <- as.factor(vb$period)
x <- with(vb, table(period, hisclass, useNA = "ifany"))
y <- prop.table(x, margin = 1) * 100
print(xtable(round(y, 1), digits = 0, caption = "Hisclass by time period, 1901--2013 (per cent)."))
@
